---
title: "Maps of State Demographics in the US for 2012."
author: "David Clark"
date: "October 6, 2015"
output: html_document
---

Load the libraries:

```{r}
library(choroplethr)
library(choroplethrMaps)
```

Look at the data for state population:

```{r}
data("df_pop_state")
head(df_pop_state)
```

Create choropleth map of US state populations:

```{r}
state_choropleth(df_pop_state, title = "State Population")
```

Create a choropleth map of per-capita income for each state.

First, lets look at the data:

```{r}
data("df_state_demographics")
colnames(df_state_demographics)
```

Now, lets make the map:

```{r}
df_state_demographics$value = df_state_demographics$per_capita_income
state_choropleth(df_state_demographics, title="Per-Capita Income")
```

Map of the percentage of the state population that is **hispanic**:

```{r}
df_state_demographics$value = df_state_demographics$percent_hispanic
state_choropleth(df_state_demographics, title = "Percent Hispanic", legend = "percentage")
```

Map of the percentage of the state population that is **asian**:

```{r}
df_state_demographics$value = df_state_demographics$percent_asian
state_choropleth(df_state_demographics, title = "Percent Asian", legend = "percentage")
```

Map of the percentage of the state population that is **black**:

```{r}
df_state_demographics$value = df_state_demographics$percent_black
state_choropleth(df_state_demographics, title = "Percent Black", legend = "percentage")
```

Map of the percentage of the state population that is **white**:

```{r}
df_state_demographics$value = df_state_demographics$percent_white
state_choropleth(df_state_demographics, title = "Percent White", legend = "percentage")
```